---
title: "Penguins Anova"
author: "Jessica Jagdeo"
date: "November 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read-in penguins.csv data

```{r, include = FALSE}

library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")

```

Our question is:

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, Adelie)?

2. Do some exploring

New functions: with + table for easy counting over multiple factors

Update species name using case_when

```{r}

counts <- with(penguins, table(Species, Sex))

penguins2 <- penguins %>%
  mutate(common_name = 
           case_when(
             Species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             Species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             Species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )
         ) %>% 
  select(-Species) %>% 
  filter(Sex == "FEMALE")

```

- Exploratory Graphs
- Summary statistics
- Levene's test for equal variances
- One-way ANOVA
- Post-hoc testing

```{r}

hists <- ggplot(penguins2, aes(x = flipper_length)) +
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~ common_name)

hists

qqs <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq() +
  facet_wrap(~ common_name)

qqs 


# Levene's test for equal variances (+2 groups... if you have 2 groups, use F-test for equal variances)

# We'll use the function leveneTest from the "car" package

# H0: Variances are equal.
# Ha: Variances unequal.

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)

penguin_levene

# We retain the null hypothesis of equal variances (p = 0.06)

variances <- penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    variances = var(flipper_length)
  )

variances



```

Part 3. One-way ANOVA

Single factor: common_name (species)
Number of levels: 3 (Chinstrap, Gentoo, Adelie)
Random variable: flipper_length (mm)

Is there a significant difference in mean flipper length (mm) for female Chinstrap, Gentoo, and Adelie penguins?

```{r}

# H0: Mean flipper lengths across all species are equal
# Ha: At least 2 means differ significantly


penguin_aov <- aov(flipper_length ~ common_name, data = penguins2)

summary(penguin_aov)

# At least 2 samples were taken from populations with different means. Which ones are different? All three different from each other? Or something else?

# Post-hoc testing using TukeyHSD

penguin_ph <- TukeyHSD(penguin_aov)

penguin_ph

```

Mean flipper lengths for Adelie, Gentoo, and Chinstrap penguins are all significantly different (F(df) = statistic, p < 0.001, $\alpha$ = 0.05 with post-hoc Tukey's HSD, $\alpha$ = 0.05. 