---
title: "Penguins Anova"
author: "Jessica Jagdeo"
date: "November 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read-in penguins.csv data

```{r, include = FALSE}

library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")

```

Our question is:

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, Adelie)?

2. Do some exploring

New functions: with + table for easy counting over multiple factors

Update species name using case_when

```{r}

counts <- with(penguins, table(Species, Sex))

penguins2 <- penguins %>%
  mutate(common_name = 
           case_when(
             Species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             Species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             Species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )
         ) %>% 
  select(-Species) %>% 
  filter(Sex == "FEMALE")

```

- Exploratory Graphs
- Summary statistics
- Levene's test for equal variances
- One-way ANOVA
- Post-hoc testing

